Drones in Wind

### 2017-07-24 Papers/DroneInTheWind.tex
minor formatting changes

Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being pitch rate and the second being thrust.  Note here that the thrust is augmented by the equilibrium condition for hover, $f = mg$.  $K$ is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.

>>>>

Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being thrust and the second being pitch rate.  Note here that the thrust is augmented by the equilibrium condition for hover, $f = mg$.  K is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.
